Investigating the alternative prey hypothesis with the POMP framework

### 2024-04-22 draft.Rmd
changes to draft

Csnippet("

") -> rproc

@@

mod <- pomp(rprocess = euler(step, delta.t =),
            times = "year", t0 = 1872,
            rinit = rinit,
            rprocess = eurler(step, delta.t=),
            rmeasure = rmeas, 
            dmeasure = , 
            paramnames = c("rho", "theta", "delta"),

@@

>>>>

@@

mod <- pomp(rprocess = euler(step, delta.t = 1/52),
            times = "year", t0 = 1872,
            rinit = rinit,
            rprocess = euler(step, delta.t=),
            rmeasure = rmeas, 
            dmeasure = , 
            paramnames = c("rho", "theta", "delta"),

@@

- `rinit`: simulator for the initial-state distiburution, i.e., the distribution of the latent state at time $t_0$
